\documentclass[11pt]{article}

\newcommand{\titrechapitre}{}%DNL -- Statistics}
\newcommand{\titreclasse}{}%Lycée Jean-Baptiste \textsc{Corot}}
\newcommand{\pagination}{}%/\pageref{LastPage}}
\newcommand{\topbotmargins}{2cm}
\newcommand{\spacebelowexo}{5mm}
\input{/home/erou/teaching/corot/latex/layout-color.tex}
%\input{layout-nb.tex}

\title{}
\date{}
\author{}

\begin{document}
\selectlanguage{english}

\noindent In a neighborhood of London, highschool students pass their A-levels. In 2023,
$1446$ women obtained the A-level, whereas $1368$ men obtained theirs. 
\begin{enumerate}
  \item \begin{enumerate}
      \item Which group performed best, men or women?
      \item But does this result really make sense?
    \end{enumerate}
\end{enumerate}
\noindent We now know that they were $1647$ women who took the examination.
There were also $1542$ men.
\begin{enumerate}
\setcounter{enumi}{1}
  \item Does this change the answer? Why?
\end{enumerate}
\noindent Finally, we obtain even more information. Many subjects can be studied
in order to obtain the A-level. In order to simplify, let us consider that
students fall into one of the categories ``Humanities'', ``Economics'' and
``Sciences''.
\begin{itemize}
  \item In humanities \begin{itemize}
      \item $321$ women obtained their A-level out of $419$.
      \item $187$ men obtained their A-level out of $250$.
    \end{itemize}
  \item In Economics
    \begin{itemize}
      \item $448$ women obtained their A-level out of $521$.
      \item $393$ men obtained their A-level out of $451$.
    \end{itemize}
  \item In Sciences \begin{itemize}
      \item $667$ women obtained their A-level out of $707$.
      \item $788$ men obtained their A-level out of $841$.
    \end{itemize}
\end{itemize}
\begin{enumerate}
\setcounter{enumi}{2}
  \item Who performed best in Humanities ? Economics ? Sciences ?
  \item Try to explain why the result is different when we look at the numbers
    without knowledge of the subjects studied.
\end{enumerate}


\end{document}
